Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-17 results.tex
Spelling correction
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1104 ccdd05d5-56c1-461a-bf98-85f6876523b4
Reword
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1105 ccdd05d5-56c1-461a-bf98-85f6876523b4

We are now prepared to offer the estimated computational cost of filtering this
sub-bank of templates compared to other methods.  We used the results of the
previous subsections to set the \SVD\ tolerance at $\left(1-10^{-4}\right)$ and the
interpolation filter length to 16. Table \ref{table:flops} shows the computational cost
in \flops\ for this sub-bank.  Fort the \FD\ method, an \fft\ block size of $\fftblock = 
2 \tmpsamps$ is assumed, resulting in a latency of $\left(\tmpsamps f^0\right)$
seconds.  Both the \FD\ method and \lloid\ are five orders of magnitude faster than
the conventional \TD\ method.  However, the \FD\ method has a latency of over half of an
hour, whereas \lloid\ has no latency at all.
%
\begin{table}
\caption{\label{table:flops}Computational cost in \flops\ of the \TD\ method, the \FD\ method, and \lloid\ for the sub-bank described in section~\ref{sec:bank-setup}.}
\begin{center}
\begin{tabular}{lll}
\tableline\tableline
method & \flops\ & latency (s) \\
\tableline
time domain & $2.4\times10^{13}$ & 0 \\
frequency domain & $2.6\times10^8$ & 2201 \\
\lloid\ (this work) & $4.7\times10^8$ & 0 \\
\tableline
\end{tabular}
\end{center}
\end{table}

@@

Table~\ref{table:flops} shows that the \lloid\ method requires $\sim$$10^8$
\flops\ to cover a sub-bank comprising $\sim$$10^2$ out of the total $\sim$$10^5$
mass pairs.  Given that modern (ca. 2011) workstations can sustain computation
rates up to $\sim$$10^{10}$ \flops{}, and assuming that other regions of the
parameter space have similar computational scaling, an entire search could be
implemented with $\gtrsim$$10$ machines.  The lengths of templates does vary
over the parameter space; lower-mass templates are longer and would require
more computation to analyze while higher-mass templates are shorter and would
require less. However, we consider the estimates based on this sub-bank to be a
reasonable representation.

>>>>

We are now prepared to offer the estimated computational cost of filtering this
sub-bank of templates compared to other methods.  We used the results of the
previous subsections to set the \SVD\ tolerance at $\left(1-10^{-4}\right)$ and the
interpolation filter length to 16. Table \ref{table:flops} shows the computational cost
in \flops\ for this sub-bank.  For the \FD\ method, an \fft\ block size of $\fftblock = 
2 \tmpsamps$ is assumed, resulting in a latency of $\left(\tmpsamps f^0\right)$
seconds.  Both the \FD\ method and \lloid\ are five orders of magnitude faster than
the conventional \TD\ method.  However, the \FD\ method has a latency of over half of an
hour, whereas \lloid\ has no latency at all.
%
\begin{table}
\caption{\label{table:flops}Computational cost in \flops\ of the \TD\ method, the \FD\ method, and \lloid\ for the sub-bank described in section~\ref{sec:bank-setup}.}
\begin{center}
\begin{tabular}{lll}
\tableline\tableline
method & \flops\ & latency (s) \\
\tableline
time domain & $2.4\times10^{13}$ & 0 \\
frequency domain & $2.6\times10^8$ & 2201 \\
\lloid\ (this work) & $4.7\times10^8$ & 0 \\
\tableline
\end{tabular}
\end{center}
\end{table}

@@

Table~\ref{table:flops} shows that the \lloid\ method requires $\sim$$10^8$
\flops\ to cover a sub-bank comprising $\sim$$10^2$ out of the total $\sim$$10^5$
mass pairs.  Given that modern (ca. 2011) workstations can sustain computation
rates up to $\sim$$10^{10}$ \flops{}, and assuming that other regions of the
parameter space have similar computational scaling, an entire search could be
implemented with $\gtrsim$$10$ machines.  Template length does vary
over the parameter space; lower-mass templates are longer and would require
more computation to analyze while higher-mass templates are shorter and would
require less. However, we consider the estimates based on this sub-bank to be a
reasonable representation.
